Phoneme surprisal

### 2019-06-18 surprisal/phoneme_surprisal.Rmd
ipas from text

```{r espeak pipeline}
# all thanks to Mika Braginsky and Dan Yurovsky
lang_codes <- list(
  "Croatian" = "hr",
  "Danish" = "da",
  "English (American)" = "en-us",
  "French (Quebec)" = "fr",
  "Italian" = "it",
  "Norwegian" = "no",
  "Russian" = "ru",
  "Spanish (Mexican)" = "es",
  "Swedish" = "sv",
  "Turkish" = "tr", 
  "Mandarin" = "cmn"
)

get_ipa <- function(word) {
  system2("espeak", args = c("--ipa=3", "-v", "en", "-q", glue("'{word}'")),
          stdout = TRUE) %>%
    gsub("^ ", "", .) %>%
    gsub("[ˈˌ]", "", .)
}
```

@@

words <- adult_utterances$word %>% 
  unique()

ipa <- words %>%
  lapply(get_ipa)

adult_utterances %<>%
  left_join(ipa) %>%
  unnest_tokens(phon, word, token = stringr::str_split, pattern = "", drop = F) %>%
  group_by(utterance_id, word) %>%
  mutate(phon_order = 1:n()) %>%
  mutate(word_length = max(phon_order)) %>%
  ungroup()

>>>>

```{r espeak pipeline}
get_ipa <- function(word) {
  system2("espeak", args = c("--ipa=3", "-v", "en-us", "-q", glue('"{word}"')),
          stdout = TRUE) %>%
    gsub("^ ", "", .) %>%
    gsub("[ˈˌ]", "", .)
}
```

@@

adult_utterances %>%
  distinct(word) %>%
  # rowwise() %>%
  # mutate(ipa = get_ipa(word)) 
  pull(word) %>%
  write_lines("words.txt")

phones <- read_lines("phones.txt") %>%
  str_split(" ", simplify = F) %>%
  unlist() %>%
  unlist() %>%
  enframe(name = NULL) %>%
  filter(nchar(value) > 0)

adult_phonemes <- adult_utterances %>%
  left_join(ipa) %>%
  unnest_tokens(ipa, word, token = stringr::str_split, pattern = "_", drop = F) %>%
  group_by(utterance_id, word) %>%
  mutate(phon_order = 1:n()) %>%
  mutate(word_length = max(phon_order)) %>%
  ungroup()
